### 2016-06-22 Renormalization.tex
Counterterm Diagrams, delta ZLgl drops out

\subsection{Regularization Schemes}\label{sec:RegSchemes}
\subsubsection*{Dimensional Regularization(DREG)}
Dimensional regularization(DREG) is a very common procedure for regularizing infinities which was devised by t'Hooft and Veltman~\cite{'tHooft:1972fi}. In this scheme loop momenta, gamma- and epsilon-tensors, phase space and fields are defined in $D$ dimensions. As in every regularization scheme a parameter with mass dimension needs to be introduced. In DREG that is the $\mu$ parameter which ensures that the loop integrals still have mass dimension 4:
\begin{align}
\int \frac{\mbox{d}^4p}{(2\pi)^4} \to \mu^{4-D} \int \frac{\mbox{d}^Dp}{(2\pi)^D}.
\end{align}
One often writes $D=4-2\epsilon$. Then the divergences of the loop integral manifest in $\frac{1}{\epsilon}$ poles.\\
However DREG suffers a flaw in supersymmetry. As the degrees of freedom of a massless gauge boson are $D-2$ but the degrees of freedom of its superpartner are 2 there is a mismatch if $D \neq 4$. As a consequence there are $2\epsilon$ degrees of freedom associated with the gluon\footnote{These degrees of freedom are identified with scalars and are therefore referred to as $\epsilon$ scalars} which do not have a supersymmetric partner. Therefore DREG violates supersymmetry.

@@

Apart from the renormalization constant of the gauge coupling and the supersymmetry restoring counterterm these are all renormalization constants needed from squark production at next to leading order. In fact the field renormalization constants of the gluino are not needed as they drop out when summing up all three counterterm Feynman diagrams. This can be seen when writing down the matrix amplitudes for the counterterm Feynman diagrams:

@@

\mathcal{M}^{\mathrm{B}} &= -2g_s^2 \frac{\left\langle v2 |P_R \slashed{k}_3|u1\right\rangle}{t_{\tilde{g}}} T^a_{13} T^a_{24} + 2g_s^2 \frac{\left\langle v2 |P_L \slashed{k}_3|u1\right\rangle}{u_{\tilde{g}}} T^a_{14} T^a_{23}\\
\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}} &= 2 \mathcal{M}^B  \left( \frac{\delta \hat{g}_s}{\hat{g}_s} \frac{\delta Z_q}{2} + \frac{\delta Z^L_{\tilde{g}}}{2} + \frac{\delta Z_{\tilde{q}}}{2} \right)\\
\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}} &= \hdots = 
\mathcal{M}^B \left[ \frac{-(t_{\tilde{g}})\delta Z_{\tilde{g}}^L + 2 \delta m_{\tilde{g}}m_{\tilde{g}}}{t_{\tilde{g}}}\right.\\
&\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \left. \frac{-(u_{\tilde{g}})\delta Z_{\tilde{g}}^L + 2 \delta m_{\tilde{g}}m_{\tilde{g}}}{u_{\tilde{g}}}\right]

@@

@@

	\node at (2.8,0.5) {$u$};
	\node at (2.8,-0.5) {$u$};
	\node at (5.2,0.5) {$\tilde{u}_L^\dagger$};
	\node at (5.2,-0.5) {$\tilde{u}_R^\dagger$};

@@

	\node at (6.8,0.5) {$u$};
	\node at (6.8,-0.5) {$u$};
	\node at (9.2,0.5) {$\tilde{u}_L^\dagger$};
	\node at (9.2,-0.5) {$\tilde{u}_R^\dagger$};

@@

	\node at (2.8,0.5) {$u$};
	\node at (2.8,-0.5) {$u$};
	\node at (5.2,0.5) {$\tilde{u}_L^\dagger$};
	\node at (5.2,-0.5) {$\tilde{u}_R^\dagger$};
	\node at (6.9,) {+\ \ u-channel};

@@

\caption{1-Loop-Level Counterterm Feynman diagrams for squark production in the MRSSM}

>>>>

\subsection{Regularization Schemes}\label{sec:RegSchemes}
\subsubsection*{Dimensional Regularization (DREG)}
Dimensional regularization(DREG) is a very common procedure for regularizing infinities which was devised by t'Hooft and Veltman~\cite{'tHooft:1972fi}. In this scheme loop momenta, gamma- and epsilon-tensors, phase space and fields are defined in $D$ dimensions. As in every regularization scheme a parameter with mass dimension needs to be introduced. In DREG that is the $\mu$ parameter which ensures that the loop integrals still have mass dimension 4:
\begin{align}
\int \frac{\mbox{d}^4p}{(2\pi)^4} \to \mu^{4-D} \int \frac{\mbox{d}^Dp}{(2\pi)^D}.
\end{align}
One often writes $D=4-2\epsilon$. Then the divergences of the loop integral manifest in $\frac{1}{\epsilon}$ poles.\\
However DREG suffers a flaw in supersymmetry. As the degrees of freedom of a massless gauge boson are $D-2$ but the degrees of freedom of its superpartner are 2 there is a mismatch if $D \neq 4$. As a consequence there are $2\epsilon$ degrees of freedom associated with the gluon\footnote{These degrees of freedom are identified with scalars and are therefore referred to as $\epsilon$ scalars} which do not have a supersymmetric partner. Therefore DREG violates supersymmetry.

@@

Apart from the renormalization constant of the gauge coupling and the supersymmetry restoring counterterm these are all renormalization constants needed from squark production at next to leading order. In fact the field renormalization constants of the gluino are not needed as they drop out when summing up all three counterterm Feynman diagrams. This can be seen when writing down the matrix amplitudes for the counterterm Feynman diagrams shown in fig. \ref{fig:CounterTerm}:

@@

\mathcal{M}^{\mathrm{B}} &= -2g_s^2 \frac{\left\langle v_2 |P_R \slashed{k}_3|u_1\right\rangle}{t_{\tilde{g}}} T^a_{\delta \beta} T^a_{\gamma \alpha} + 2g_s^2 \frac{\left\langle v_2 |P_L \slashed{k}_3|u_1\right\rangle}{u_{\tilde{g}}} T^a_{\gamma\beta} T^a_{\delta\alpha}\\
\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}} &= 2 \mathcal{M}^B  \left( \frac{\delta \hat{g}_s}{\hat{g}_s} + \frac{\delta Z_q}{2} + \frac{\delta Z^L_{\tilde{g}}}{2} + \frac{\delta Z_{\tilde{q}}}{2} \right)\\
\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}} &= 2g_s^2 \left\langle v_2 \left| P_R\ i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} \left[  i(\delta Z_{\tilde{g}}^L P_L + \delta Z_{\tilde{g}}^L P_L)\slashed{p}  \right.\right.\right.\nonumber\\
& \hspace{2cm}\left.\left.\left.\left. -i\left( \frac{\delta Z_{\tilde{g}}^L + \delta Z_{\tilde{g}}^R}{2}m_{\tilde{g}} + \delta m_{\tilde{g}} \right) \right]i\frac{\slashed{p}+m_{\tilde{g}}}{t_{\tilde{g}}} P_L \right|u_1\right\rangle\right|_{p = p_1-p_3} + \mathrm{u-channel}\nonumber\\
&= -\mathcal{M}^B  \delta Z_{\tilde{g}}^L + 2  \frac{ m_{\tilde{g}}}{t_{\tilde{g}}} \left( -2g_s^2 \frac{\left\langle v_2 |P_R \slashed{k}_3|u_1\right\rangle}{t_{\tilde{g}}} T^a_{\delta \beta} T^a_{\gamma \alpha} \right)\delta m_{\tilde{g}}\nonumber\\ 
& \hspace{2cm}+ 2 \frac{ m_{\tilde{g}}}{u_{\tilde{g}}} \left( 2g_s^2 \frac{\left\langle v_2 |P_L \slashed{k}_3|u_1\right\rangle}{u_{\tilde{g}}} T^a_{\gamma\beta} T^a_{\delta\alpha} \right)\delta m_{\tilde{g}}.

@@

Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks the renormalization constant for the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added. This is also true in a more general case, i.e. the renormalization constants of virtual particles do always drop out.

@@

	\node at (2.7,0.5) {$u_\alpha$};
	\node at (2.7,-0.5) {$u_\beta$};
	\node at (5.4,0.5) {$\tilde{u}_{L\gamma}^\dagger$};
	\node at (5.4,-0.5) {$\tilde{u}_{R\delta}^\dagger$};

@@

	\node at (6.7,0.5) {$u_\alpha$};
	\node at (6.7,-0.5) {$u_\beta$};
	\node at (9.4,0.5) {$\tilde{u}_{L\gamma}^\dagger$};
	\node at (9.4,-0.5) {$\tilde{u}_{R\delta}^\dagger$};

@@

	\node at (2.6,0.5) {$u_\alpha$};
	\node at (2.6,-0.5) {$u_\beta$};
	\node at (5.3,0.5) {$\tilde{u}_{L\gamma}^\dagger$};
	\node at (5.3,-0.5) {$\tilde{u}_{R\delta}^\dagger$};
	\node at (6.9,0) {+\ \ u-channel};

@@

\caption{1-Loop-level counterterm Feynman diagrams for squark production in the MRSSM. The Greek latters label the particle's color.}\label{fig:CounterTerm}
